\textbf{NBA Party}

### 2017-07-07 init_model.rnw
Now retiring this script, as it was getting too long. Code was ported over to init_draft.r.

@@

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/population_by_MSA_year.RData')
load(file = 'tmp_data/studios_and_artists_nba.RData')

@@

### This is simply ad-hoc.
musicians[, population := 0.0]
for (i in 1:nrow(musicians))
    set(musicians, i, j = 'population', 
        value = pop[grepl(musicians[i, locality], locality) &
                    grepl(musicians[i, state],    locality) &
                    musicians[i, season] == season, mean(population)])

@@

\subsection{Lines data} We obtained data from \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{Covers.com}, which records the outcome of each game alongside the line set by a betting house.
<<echo=F>>=
nba.lines <- lines
nba.lines[, list(date = as.Date(date), team, opponent, line, score)]
@

@@

<<echo=F>>=
### Merge lines data with BLS data.
nba.lines <- merge(nba.lines, musicians,
               by.x = c('season', 'last.game.loc'),
               by.y = c('season', 'team'), all.x = T)

@@

<<echo=F>>= 
musicians[, list(average.nmusicians = mean(nmusicians) %>% round(., digits = 1)),
          by = team][order(average.nmusicians)][c(1:5, 25:27)]
@

@@

### We then create a continuous measure of nightlife. We rescale to 0-1 so it's comparable.
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party := party / max(party, na.rm = T)]

@@

##################################################
### Dot plot of Party-Continuous by Team Location
##################################################
tmp <- musicians[, list(party.continuous = mean(log(nmusicians+1))), 
                 by = team][order(party.continuous)][!is.na(party.continuous)]

@@

stargazer(mp, covariate.labels = c('Party placebo', 'Lag changes in posession', 
                                   'Logged travel distance', 'East-west travel direction', 
                                   'Number hours rest time', 'Time of game during day', 
                                   'Home team effect', 'Logged travel distance * east-west', 
                                   'Constant'),
          dep.var.labels = 'Meet the Spread (NBA)')

@@

##################################################
### Why drinking estabs doesn't work. (NBA)
##################################################
load(file = 'tmp_data/alcohol_and_drinking_nba.RData')
drinking <- copy(dt)
setnames(drinking, 'variable', 'ndrinks')
rm(dt)

tmpm <- nba.lines[, list(log.nmusicians = mean(log(nmusicians+1), na.rm = T),
                         log.population = mean(log(population+1), na.rm = T)), 
                  by = team][order(log.nmusicians)] %>% na.omit
tmpd <- drinking[, list(log.ndrinks = mean(log(ndrinks+1))), 
                  by = team][order(log.ndrinks)] %>% na.omit
tmp <- merge(tmpm, tmpd, by = 'team')
setorder(tmp, log.nmusicians)

pdf('writing/why_drinks_or_population_dont_work.pdf', width = 16, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$log.nmusicians,
     main = 'Why drinking establishments or population don\'t work as a proxy for nightlife',
     ylab = 'Log sum of Variable',
     xlab = '', axes = F, pch = 1, ylim = c(0, max(tmp$log.population)), type = 'l')
points(x = ticks, y = tmp$log.ndrinks, pch = 16, col = 'purple', type = 'l')
points(x = ticks, y = tmp$log.population, pch = 18, col = 'orange', type = 'l')
### Houston has large population, but isn't necessarily known for nightlife.
segments(x0 = which(tmp$team == 'houston rockets'), 
         x1 = which(tmp$team == 'houston rockets'),
         y0 = -1,
         y1 = tmp[team == 'houston rockets', log.population], col = 'gray70', lty = 'dashed')
segments(x0 = which(tmp$team == 'houston rockets'), 
         x1 = length(ticks),
         y0 = tmp[team == 'houston rockets', log.population],
         y1 = tmp[team == 'houston rockets', log.population], col = 'gray70', lty = 'dashed')
abline(h = tmp[team == 'houston rockets', log.ndrinks], col = 'gray70', lty = 'dashed')
### New orleans is infamous for party, but Population places it at the bottom of the index.
segments(x0 = which(tmp$team == 'new orleans hornets'),
         x1 = which(tmp$team == 'new orleans hornets'), 
         y0 = -1, 
         y1 = tmp[team == 'new orleans hornets', log.population],col = 'gray70', lty = 'dashed')
segments(x0 = 0, x1 = which(tmp$team == 'new orleans hornets'),
         y0 = tmp[team == 'new orleans hornets', log.population],
         y1 = tmp[team == 'new orleans hornets', log.population], col = 'gray70', lty = 'dashed')
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>%
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
legend(x = 1.5, y = 12.5, legend = c('Musicians and sound recording studios',
                                 'Drinking establishments and liquor stores',
                                 'Population'), pch = c(1, 16, 18), col = c('black', 'purple', 'orange'))
text(x = 3.6, y = 9.5, labels = paste("Correlation (alcohol):       ", 
                                       cor(tmp$log.nmusicians, tmp$log.ndrinks) %>% round(., 3)))
text(x = 3.6, y = 10, labels = paste("Correlation (population): ", 
                                       cor(tmp$log.nmusicians, tmp$log.population) %>% round(., 3)))
points(x = c(which(tmp$team == 'new orleans hornets'),
             which(tmp$team == 'houston rockets'),
             which(tmp$team == 'houston rockets')),
       y = c(tmp[team == 'new orleans hornets', log.population],
             tmp[team == 'houston rockets', log.population],
             tmp[team == 'houston rockets', log.ndrinks]),
       type = 'p', col = 'red')
dev.off()

@@

HOURS <- 36
m <- glm(outcome == 'W' ~ party, 
         data = nba.lines[season < 2016 & last.game.loc != team])

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = nba.lines[season == 2016 & nhours.lgame <= HOURS & 
                                last.game.loc != team], type = 'response')

idx <- which(p < 0.476)
out <- table(nba.lines[season == 2016 & nhours.lgame <= HOURS & last.game.loc != team][idx, outcome])

(out['L'] * 100 - 110*out['W']) %>% as.numeric

table(round(p), nba.lines[season == 2016 & nhours.lgame <= HOURS & 
                      last.game.loc != team, outcome])

@@

<<echo=1>>=
source('functions.r')
m <- glm(outcome == 'W' ~ party,
         data = nba.lines[season < 2016 & last.game.loc != team])

p <- predict(m, newdata = nba.lines[season == 2016 & nhours.lgame <= HOURS & 
                                last.game.loc != team], type = 'response')

table(round(p), nba.lines[season == 2016 & nhours.lgame <= HOURS & 
                      last.game.loc != team, outcome])

@@

### Points  allowed as afunction of last game location (by party)
nba.lines[, demeaned.pts.admitted := team.pts.admitted - mean(team.pts.admitted), by = list(season, team)]
nba.lines[, mean(demeaned.pts.admitted), by = list(last.game.loc, party.discrete)][order(V1)]
mpa1 <- lm(demeaned.pts.admitted ~ party.discrete, data = nba.lines)

@@

<<echo=-1>>=
load(file = 'tmp_data/covers_lines_mlb.RData')
mlb.lines <- lines

@@

pdf('writing/next_day_opponent_mlb.pdf', width = 14, height = 14)
ggplot(tmp, aes(x = location, y = last.game.loc, fill = log(N))) + 
    geom_tile() +
    facet_wrap(~lst.game + cur.game) + 
    labs(x = 'Current Game Location', y = 'Last Game Location', 
         title = 'Distribution of Next Day Opponent - MLB') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 315, vjust = 0.5),
          plot.title = element_text(hjust=.5))
dev.off()

##################################################
### Party by team location
##################################################
load(file = 'tmp_data/studios_and_artists_mlb.RData')
setnames(dt, 'variable', 'nmusicians')

tmp <- dt[, list(party.continuous = mean(log(nmusicians+1))),
          by = team][order(party.continuous)][!is.na(party.continuous)]

pdf('writing/Party_by_Team_Location_mlb.pdf', width = 14, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$party.continuous, 
     main = 'Continuous measure of party by Team Location: MLB',
     ylab = 'Log sum of Musicians and Sound Recording Studios',
     xlab = '',
     axes = F)
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
dev.off()

@@

pdf('writing/mlb_bets_by_season.pdf')
par(mfrow = c(3,2))
b <- lapply(2012:2016, function(yr) {
    m <- glm(I(team.score > opponent.score) ~ party + odds,
             data = mlb.lines[season < yr], family = 'binomial')
    p <- predict(m, newdata = mlb.lines[year(date) == yr], type = 'response')
    ### Subset data to relevant year we wish to predict on; make predictions.
    tmp <- mlb.lines[season == yr, .(matchup, date, team, opponent, 
                                     team.score, opponent.score, odds)]
    tmp[, fitted := predict(m, newdata = mlb.lines[year(date) == yr], type = 'response')]
    ### Realize that we can only make one prediction per game. So take the stronger bet.
    setkey(tmp, date, matchup)
    tmp <- tmp[, .SD[which.max(abs(fitted - .5))], by = list(matchup, date)]
    tmp <- mlb.lines[tmp, on = intersect(names(tmp), names(mlb.lines))]
    ### Translate fitted probabilities into 0-1 predictions if our odds differ by threshold amount.
    tmp[, prediction := mapply(hangover::Predict, prediction = tmp$fitted, vegas = tmp$odds, 
                               MoreArgs = list(threshold = 0.02))] # 0.02 was chosen ad-hoc.
    tmp <- tmp[!is.na(prediction)]
    ### Translate prediction into a monetary gain or loss based on odds and actual outcome.
    tmp[, bet := mapply(hangover::Bet, our.prediction = prediction, 
                        actual.outcome = team.score > opponent.score,
                        odds = odds)]
    ### Plot the cumulative sum of profits over the course of the season.
    tmp[, running.prof := cumsum(bet)]    
    cat(paste0(sum(tmp$bet), '\n'))
    plot(x = 1:nrow(tmp), y = tmp$running.prof, 
         main = paste0('Profit over the ', yr, ' season: $', 
                       format(round(sum(tmp$bet), digits = -1), big.mark = ','), '\n',
                       'Training on 2011-', yr-1, ' data'),
         xlab = 'Game Number', ylab = 'Profit', type = 'l')
    abline(a = 0, b = 0, lty = 3)
    points(x = which.min(tmp$running.prof), y = min(tmp$running.prof), type = 'p')
    text(x = which.min(tmp$running.prof), y = min(tmp$running.prof), 
         labels = round(min(tmp$running.prof)), pos = 4)
    return(tmp[, bet])
})
dev.off()

### Meet the spread for both NBA and MLB
pdf('writing/meet_the_spread.pdf')
par(mfcol = c(2, 1))
tmp <- nba.lines[, list(meet.spread = mean(outcome == 'W')), 
          by = list(season, team)]
hist(tmp$meet.spread, prob = T, main = paste('How often do teams meet the spread? (NBA)', 
                                             'By season-team, 2010-11 through 2016-17',
                                             sep = '\n'),
     xlab = 'Meet the Spread', breaks = 25)
lines(density(tmp$meet.spread, adjust = 2), col = 'orange', lty = 'dashed', lwd = 3)
### There should be 'no information' left over after conditioning on odds.
noinf <- lm(I(team.score > opponent.score) ~ odds, data = mlb.lines)
preds <- fitted(noinf)
mlb.lines[, fitted := fitted(noinf)]
mlb.lines[, resid  := resid(noinf)]
tmp <- mlb.lines[, .(avg.residual = mean(resid)), by = .(fitted = round(fitted, 3))]
plot(x = tmp$fitted, y = tmp$avg.residual, 
     xlab = 'Fitted Probability', ylab = 'Average Residual', 
     main = paste('After conditioning on bookkeeper\'s odds (MLB),',
                  'successful prediction is a coin-flip', sep = '\n'))
abline(lm(avg.residual ~ fitted, tmp), col = 'orange', lty = 'dashed', lwd = 3)
dev.off()

@@

>>>>

Sys.setlocale('LC_ALL','C')  # Needed for population data (within area.title variable)

@@

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/population_by_MSA_year.RData')
load(file = 'tmp_data/studios_and_artists.RData')

@@

load(file = 'tmp_data/alcohol_and_drinking.RData')
drinking <- copy(dt)
rm(dt)
setnames(drinking, 'variable', 'ndrinks')

musicians <- merge(musicians, drinking, on = intersect(names(musicians), names(drinking)))

### Geocode team locations. Prepare data for merge.
locs <- MyGeoCode(unique(lines$team), 'nba')
states <- data.table(state = state.name, state.abb = state.abb)
states <- rbind(states, data.frame(state = 'District of Columbia', state.abb = 'DC'))
locs <- locs[states, on = 'state', nomatch = 0]

### We can't simply merge. We have to look for the county within the MSA.
musicians[, area.title := gsub(' msa$', '', area.title, ignore.case = T)]
musicians <- lapply(1:nrow(locs), function(i) { 
    matched <- musicians[grepl(locs[i, locality],  area.title, ignore.case = T) &
                         grepl(locs[i, state.abb], area.title, ignore.case = T)]
    matched[, c('locality', 'state') := locs[i, list(locality, state.abb)]]
    return(matched)
}) %>% rbindlist %>% unique

demog <- merge(musicians, pop, by = c('area.title', 'year'), all.x = T)
setnames(demog, 'state', 'state.abb')

lines <- lines[locs, on = 'team']  # Here, we lose Toronto (that's OK).

setnames(demog, 'year', 'season')
demog[, season := season + 1]

nba.lines <- lines[demog, on = c('locality', 'state.abb', 'season'), allow.cartesian = T]

nba.lines <- nba.lines[last.game.loc != 'toronto raptors' &
                       location      != 'toronto raptors']

@@

\subsection{Lines data} We obtained data from \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{Covers.com}, which records the outcome of each game alongside the line set by a betting house.
<<echo=F>>=
#nba.lines <- lines
#nba.lines[, list(date = as.Date(date), team, opponent, line, score)]
@

@@

<<echo=F>>=

## nba.lines <- nba.lines[locs, on = 'team']

## ## setnames(nba.lines, 'state.abb', 'state')
## setnames(musicians, 'year', 'season')
## musicians[, season := as.integer(season)]
## merge(nba.lines, musicians, by = c('locality', 'state', 'season'))
## nba.lines[musicians, on = c('locality', 'state', 'season')]
## ### Merge lines data with BLS data.
## nba.lines <- merge(nba.lines, musicians,
##                by.x = c('season', 'last.game.loc'),
##                by.y = c('season', 'team'), all.x = T)

@@

<<echo=F>>= 
#musicians[, list(average.nmusicians = mean(nmusicians) %>% round(., digits = 1)),
#          by = team][order(average.nmusicians)][c(1:5, 25:27)]
@

@@

### We then create a continuous measure of nightlife. We rescale to 0-1 so it's comparable.
nba.lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians+1), 0)]
nba.lines[, party := party / max(party, na.rm = T)]
@

@@

##################################################
### Dot plot of Party-Continuous by Team Location
##################################################
## tmp <- musicians[, list(party.continuous = mean(log(nmusicians+1))), 
##                  by = team][order(party.continuous)][!is.na(party.continuous)]
tmp <- nba.lines[, list(party.continuous = mean(log(nmusicians+1))),
                 by = team][order(party.continuous)]

@@

# mp
stargazer(mp, covariate.labels = c('Party placebo', 'Lag changes in posession', 
                                   'Logged travel distance', 'East-west travel direction', 
                                   'Number hours rest time', 'Time of game during day', 
                                   'Home team effect', 'Logged travel distance * east-west', 
                                   'Constant'),
          dep.var.labels = 'Meet the Spread (NBA)')

@@

##################################################
### Why drinking estabs doesn't work. (NBA)
##################################################
## load(file = 'tmp_data/alcohol_and_drinking.RData')
## drinking <- copy(dt)
## setnames(drinking, 'variable', 'ndrinks')
## rm(dt)

## tmpm <- nba.lines[, list(log.nmusicians = mean(log(nmusicians+1), na.rm = T),
##                          log.population = mean(log(population+1), na.rm = T)), 
##                   by = team][order(log.nmusicians)] %>% na.omit
## tmpd <- drinking[, list(log.ndrinks = mean(log(ndrinks+1))), 
##                   by = team][order(log.ndrinks)] %>% na.omit
## tmp <- merge(tmpm, tmpd, by = 'team')
## setorder(tmp, log.nmusicians)

tmp <- nba.lines[, list(log.nmusicians = mean(log(nmusicians+1)),
                        log.population = mean(log(population+1)),
                        log.ndrinks    = mean(log(ndrinks+1))), by = team][order(log.nmusicians)]

pdf('writing/why_drinks_or_population_dont_work.pdf', width = 16, height = 8.5)
ticks = 1:nrow(tmp)
plot(x = ticks, 
     y = tmp$log.nmusicians,
     main = 'Why drinking establishments or population don\'t work as a proxy for nightlife',
     ylab = 'Log sum of Variable',
     xlab = '', axes = F, pch = 1, ylim = c(0, max(tmp$log.population,na.rm = T)), type = 'l')
points(x = ticks, y = tmp$log.ndrinks, pch = 16, col = 'purple', type = 'l')
points(x = ticks, y = tmp$log.population, pch = 18, col = 'orange', type = 'l')
### Houston has large population, but isn't necessarily known for nightlife.
segments(x0 = which(tmp$team == 'houston rockets'), 
         x1 = which(tmp$team == 'houston rockets'),
         y0 = -1,
         y1 = tmp[team == 'houston rockets', log.population], col = 'gray70', lty = 'dashed')
segments(x0 = which(tmp$team == 'houston rockets'), 
         x1 = length(ticks),
         y0 = tmp[team == 'houston rockets', log.population],
         y1 = tmp[team == 'houston rockets', log.population], col = 'gray70', lty = 'dashed')
abline(h = tmp[team == 'houston rockets', log.ndrinks], col = 'gray70', lty = 'dashed')
### New orleans is infamous for party, but Population places it at the bottom of the index.
segments(x0 = which(tmp$team == 'new orleans hornets'),
         x1 = which(tmp$team == 'new orleans hornets'), 
         y0 = -1, 
         y1 = tmp[team == 'new orleans hornets', log.population],col = 'gray70', lty = 'dashed')
segments(x0 = 0, x1 = which(tmp$team == 'new orleans hornets'),
         y0 = tmp[team == 'new orleans hornets', log.population],
         y1 = tmp[team == 'new orleans hornets', log.population], col = 'gray70', lty = 'dashed')
axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>%
                               gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
axis(side = 2)
legend(x = 1.5, y = 12.5, legend = c('Musicians and sound recording studios',
                                 'Drinking establishments and liquor stores',
                                 'Population'), pch = c(1, 16, 18), col = c('black', 'purple', 'orange'))
text(x = 3.6, y = 9.5, labels = paste("Correlation (alcohol):       ", 
                                       cor(tmp$log.nmusicians, tmp$log.ndrinks) %>% round(., 3)))
text(x = 3.6, y = 10, labels = paste("Correlation (population): ", 
                                       cor(tmp$log.nmusicians, tmp$log.population) %>% round(., 3)))
points(x = c(which(tmp$team == 'new orleans hornets'),
             which(tmp$team == 'houston rockets'),
             which(tmp$team == 'houston rockets')),
       y = c(tmp[team == 'new orleans hornets', log.population],
             tmp[team == 'houston rockets', log.population],
             tmp[team == 'houston rockets', log.ndrinks]),
       type = 'p', col = 'red')
dev.off()

@@

## HOURS <- 36
## m <- glm(outcome == 'W' ~ party, 
##          data = nba.lines[season < 2016 & last.game.loc != team])

## ### We're only interested in making predictions when teams party.
## p <- predict(m, newdata = nba.lines[season == 2016 & nhours.lgame <= HOURS & 
##                                 last.game.loc != team], type = 'response')

## idx <- which(p < 0.476)
## out <- table(nba.lines[season == 2016 & nhours.lgame <= HOURS & last.game.loc != team][idx, outcome])

## (out['L'] * 100 - 110*out['W']) %>% as.numeric

## table(round(p), nba.lines[season == 2016 & nhours.lgame <= HOURS & 
##                       last.game.loc != team, outcome])

@@

<<echo=1>>=
## ## source('functions.r')
## m <- glm(outcome == 'W' ~ party,
##          data = nba.lines[season < 2016 & last.game.loc != team])

## p <- predict(m, newdata = nba.lines[season == 2016 & nhours.lgame <= HOURS & 
##                                 last.game.loc != team], type = 'response')

## table(round(p), nba.lines[season == 2016 & nhours.lgame <= HOURS & 
##                       last.game.loc != team, outcome])

@@

### Points  allowed as afunction of last game location (by party)
nba.lines[, demeaned.pts.admitted := team.pts.admitted - mean(team.pts.admitted), by = list(season, team)]
nba.lines[, party.discrete := grepl("(los angeles)|(new york)|(brooklyn)", last.game.loc) &
                nhours.lgame <= HOURS &
                last.game.loc != team]

nba.lines[, mean(demeaned.pts.admitted), by = list(last.game.loc, party.discrete)][order(V1)]
mpa1 <- lm(demeaned.pts.admitted ~ party.discrete, data = nba.lines)

@@

<<echo=-1>>=
load(file = 'tmp_data/covers_lines_mlb.RData')
locs <- MyGeoCode(unique(lines$team), 'mlb')
states <- data.table(state = state.name, state.abb = state.abb)
states <- rbind(states, data.frame(state = 'District of Columbia', state.abb = 'DC'))
locs <- locs[states, on = 'state', nomatch = 0]
lines <- lines[locs, on = 'team']  # Here, we lose Toronto (that's OK).
mlb.lines <- lines[demog, on = c('locality', 'state.abb', 'season'), allow.cartesian = T]

@@

## pdf('writing/next_day_opponent_mlb.pdf', width = 14, height = 14)
## ggplot(tmp, aes(x = location, y = last.game.loc, fill = log(N))) + 
##     geom_tile() +
##     facet_wrap(~lst.game + cur.game) + 
##     labs(x = 'Current Game Location', y = 'Last Game Location', 
##          title = 'Distribution of Next Day Opponent - MLB') +
##     theme_bw() +
##     theme(axis.text.x = element_text(angle = 315, vjust = 0.5),
##           plot.title = element_text(hjust=.5))
## dev.off()

##################################################
### Party by team location
##################################################
## load(file = 'tmp_data/studios_and_artists_mlb.RData')
## setnames(dt, 'variable', 'nmusicians')

tmp <- mlb.lines[, list(party.continuous = mean(log(nmusicians+1))),
                 by = team][order(party.continuous)][!is.na(party.continuous)]

## pdf('writing/Party_by_Team_Location_mlb.pdf', width = 14, height = 8.5)
## ticks = 1:nrow(tmp)
## plot(x = ticks, 
##      y = tmp$party.continuous, 
##      main = 'Continuous measure of party by Team Location: MLB',
##      ylab = 'Log sum of Musicians and Sound Recording Studios',
##      xlab = '',
##      axes = F)
## axis(side = 1, at = ticks, labels = gsub('([a-z]{4,}) ', '\\1\n', tmp$team) %>% 
##                                gsub('([a-z]{6})[a-z]{1,}', '\\1', .), las = 2, xpd = NA)
## axis(side = 2)
## dev.off()

@@

pdf('writing/mlb_bets_by_season.pdf')
par(mfrow = c(3,2))
b <- lapply(2012:2016, function(yr) {
    m <- glm(I(team.score > opponent.score) ~ party + odds,
             data = mlb.lines[season < yr], family = 'binomial')
    p <- predict(m, newdata = mlb.lines[year(date) == yr], type = 'response')
    ### Subset data to relevant year we wish to predict on; make predictions.
    tmp <- mlb.lines[season == yr, .(matchup, date, team, opponent, 
                                     team.score, opponent.score, odds)]
    tmp[, fitted := predict(m, newdata = mlb.lines[season == yr], type = 'response')]
    ### Realize that we can only make one prediction per game. So take the stronger bet.
    setkey(tmp, date, matchup)
    tmp <- tmp[, .SD[which.max(abs(fitted - .5))], by = list(matchup, date)]
    tmp <- mlb.lines[tmp, on = intersect(names(tmp), names(mlb.lines))]
    ### Translate fitted probabilities into 0-1 predictions if our odds differ by threshold amount.
    tmp[, prediction := mapply(hangover::Predict, prediction = tmp$fitted, vegas = tmp$odds, 
                               MoreArgs = list(threshold = 0.02))] # 0.02 was chosen ad-hoc.
    tmp <- tmp[!is.na(prediction)]
    ### Translate prediction into a monetary gain or loss based on odds and actual outcome.
    tmp[, bet := mapply(hangover::Bet, our.prediction = prediction, 
                        actual.outcome = team.score > opponent.score,
                        odds = odds)]
    ### Plot the cumulative sum of profits over the course of the season.
    tmp[, running.prof := cumsum(bet)]    
    cat(paste0(sum(tmp$bet), '\n'))
    plot(x = 1:nrow(tmp), y = tmp$running.prof, 
         main = paste0('Profit over the ', yr, ' season: $', 
                       format(round(sum(tmp$bet), digits = -1), big.mark = ','), '\n',
                       'Training on 2011-', yr-1, ' data'),
         xlab = 'Game Number', ylab = 'Profit', type = 'l')
    abline(a = 0, b = 0, lty = 3)
    points(x = which.min(tmp$running.prof), y = min(tmp$running.prof), type = 'p')
    text(x = which.min(tmp$running.prof), y = min(tmp$running.prof), 
         labels = round(min(tmp$running.prof)), pos = 4)
    return(tmp[, bet])
})
dev.off()

### Meet the spread for both NBA and MLB
pdf('writing/meet_the_spread.pdf')
par(mfcol = c(2, 1))
tmp <- nba.lines[, list(meet.spread = mean(outcome == 'W')), 
          by = list(season, team)]
hist(tmp$meet.spread, prob = T, main = paste('How often do teams meet the spread? (NBA)', 
                                             'By season-team, 2010-11 through 2016-17',
                                             sep = '\n'),
     xlab = 'Meet the Spread', breaks = 25)
lines(density(tmp$meet.spread, adjust = 2), col = 'orange', lty = 'dashed', lwd = 3)
### There should be 'no information' left over after conditioning on odds.
mlb.lines <- na.omit(mlb.lines)
noinf <- lm(I(team.score > opponent.score) ~ odds, data = mlb.lines)
preds <- fitted(noinf)
mlb.lines[, fitted := fitted(noinf)]
mlb.lines[, resid  := resid(noinf)]
tmp <- mlb.lines[, .(avg.residual = mean(resid)), by = .(fitted = round(fitted, 3))]
plot(x = tmp$fitted, y = tmp$avg.residual, 
     xlab = 'Fitted Probability', ylab = 'Average Residual', 
     main = paste('After conditioning on bookkeeper\'s odds (MLB),',
                  'successful prediction is a coin-flip', sep = '\n'))
abline(lm(avg.residual ~ fitted, tmp), col = 'orange', lty = 'dashed', lwd = 3)
dev.off()

@@

### Musicians by area.
## load(file = 'tmp_data/studios_and_artists.RData')
## tmp <- demog[, list(log.nmusicians = log(nmusicians + 1),
##                       log.ndrinks    = log(ndrinks    + 1),
##                       log.population = log(population + 1)), by = locality][order(log.nmusicians)]
## points(demog[, log(nmusicians + 1)])
